---
title: "Methods"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("R/read_manifest.R")
source("R/read_summary.R")

result_dir <- "data"
manifest <- read_manifest(result_dir)
```

## Analysis Parameters

The following parameters were used for this analysis:

| Parameter | Value |
|-----------|-------|
| **Pipeline Version** | `r manifest$pipeline_version` |
| **Project Name** | `r manifest$project_name` |
| **Species TaxID** | `r manifest$species_tax_id` |
| **Integration Method** | `r manifest$integration_method` |
| **Samples** | `r paste(manifest$samples, collapse = ", ")` |
| **Groups** | `r paste(manifest$groups, collapse = ", ")` |

## Methods Paragraph

Single-cell RNA-seq data were processed using **scRNAseqMulticommand** (`r manifest$pipeline_version`). Cells were filtered based on mitochondrial content and gene count thresholds. Dimensionality reduction, clustering, and integration were performed using Seurat (`r manifest$integration_method` integration). Marker genes were identified using the Wilcoxon rank-sum test. Cell type annotation was performed using SingleR. Ambient RNA contamination was assessed using decontX.

## Output Files

```{r output-files}
if (!is.null(manifest$final_objects) && length(manifest$final_objects) > 0) {
  objs <- do.call(rbind, lapply(manifest$final_objects, as.data.frame, stringsAsFactors = FALSE))
  knitr::kable(objs, format = "html")
} else {
  cat("No final output objects recorded.")
}
```
