---
title: "Project Overview"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
source("R/read_manifest.R")
source("R/read_summary.R")
source("R/tables.R")

result_dir <- "data"
if (!dir.exists(result_dir) || !file.exists(file.path(result_dir, "manifest.json"))) {
  stop("Pipeline output not found. Please link or copy results to report/data/")
}

manifest <- read_manifest(result_dir)
```

## Project Summary

This report summarizes the scRNA-seq analysis generated by **scRNAseqMulticommand**.

| Field | Value |
|------|-------|
| **Project** | `r manifest$project_name` |
| **Pipeline Version** | `r manifest$pipeline_version` |
| **Species TaxID** | `r manifest$species_tax_id` |
| **Integration Method** | `r manifest$integration_method` |
| **Run Timestamp** | `r manifest$run_timestamp` |
| **Samples** | `r paste(manifest$samples, collapse = ", ")` |
| **Groups** | `r paste(manifest$groups, collapse = ", ")` |

## Pipeline Steps

```{r steps-table}
knitr::kable(render_steps_table(manifest), format = "html")
```

## Final Outputs

```{r final-objects}
if (!is.null(manifest$final_objects) && length(manifest$final_objects) > 0) {
  objs <- do.call(rbind, lapply(manifest$final_objects, as.data.frame, stringsAsFactors = FALSE))
  knitr::kable(objs, format = "html")
} else {
  cat("No final output objects recorded in manifest.")
}
```
